---
title: "hw1"
author: "Jack Chen, Sharon Zhao, Alex Makhratchev"
date: "1/13/2022"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
cars=read.csv("mtcars.csv")
head(cars)
```
## Q1

```{r}
v1 = mean(cars$mpg)
v2 = mean(cars$cyl)
v3 = mean(cars$disp)
v4 = mean(cars$hp)
v5 = mean(cars$drat)
v6 = mean(cars$wt)
v7 = mean(cars$qsec)
v8 = mean(cars$vs)
v9 = mean(cars$am)
v10 = mean(cars$gear)
v11 = mean(cars$carb)
tab <- matrix(c(v1, v2, v3, v4, v5, v6, v7, v8, v9, v10, v11), ncol=11)
colnames(tab) <- c("mpg", "cyl", "disp", "hp", "drat", "wt", "qsec", "vs", "am", "gear", "carb")
rownames(tab) <- c("mean")
library(knitr)
kable(tab)
```

## Q2

```{r}
df = as.data.frame(cars)
df <- df[ , -which(names(df) %in% c("model"))]
result_1 = cov(df)
result_2 = cor(df)
result_1
result_2
```
### Explanation: 
Based on the variance-covariance matrix, it can be interpreted that the diagonal is the variance of the
variable. A positive covariance means that two variables increase or decrease at the same time. For example,
the covariance of disp and cyl is 199.66028 which means when disp increases cyl tends to increase too. Some
other pairs of variable that have a positive covariance are hp and cyl, qsec and mpg, and drat and vs. A
negative covariance means that two variables means that when one of the variables increases the other one
decreases. Some examples are disp and mpg whose covariance is -633.09721, drat and cyl whose covariance is
-0.69993811, and hp and qsec whose covariance is -0.70822339. 
The correlation matrix tells us the correlation between two variables. A large and positive correlation means
that two variables have a strong correlation and that they increase simultaneously. Examples for strong
positive correlations are drat and mpg, disp and cyl, carb and hp. A small correlation that is close to 0
means that two variables are unlikely to be correlated. Pairs of variables that are not correlated are am and
hp, qsec and wt, gear and vs. Negative and large correlations indicate that two variables change oppositely.
While one variable decreases, the other increases. Examples of pairs of varibles that have this correlation
are drat and wt, wt and mpg, and vs and disp. 

# Q3

```{r cars}
d = read.csv("mtcars.csv")
d
```


```{r cars2}

plot(x = d$wt,
     y = d$mpg,
     xlab = "Weight",
     ylab = "MPG",
     main = "Weight vs MGP")
```

# Q4
Blue is 4 cylinder, Purple is 6 cylinder, and Gray is 8 cylinder
```{r}
plot(x = d$wt,
     y = d$mpg,
     col = d$cyl,
     xlab = "Weight",
     ylab = "MPG",
     main = "Weight vs MGP VS # of Cylinders")
```

## Q5

```{r}
cars_num=subset(cars,select=-c(model))
pairs(cars_num, pch=20)
```

# Q6

There is a relationship between wt and mpg and it is subject to the number of cylinders. As shown in the colored scatter plot, vehicles that weigh less and have 4 cylinders have the highest MPG. The second group is the 6 cylinder vehicles with medium weight and they have medium MPG. The last group is the heavy vehicles with the most cylinders and they have the lowest MPG.

## Q7

```{r}
library(fmsb)
max_min <- data.frame(mpg = c(6, 0), cyl = c(6, 0), disp = c(6, 0), hp = c(6, 0), drat = c(6, 0), wt = c(6, 0), qsec = c(6, 0), vs = c(6, 0), am = c(6, 0), gear = c(6, 0), carb = c(6, 0))
rownames(max_min) <- c("max", "min")
df=data.frame(cars_num)
df <- log(df[ , -which(names(df) %in% c("am","vs"))])
df$vs <- cars_num$vs
df$am <- cars_num$am
df <- rbind(max_min, df)
df
radarchart(df)
```
### Explanation: 
I can't tell from the chart since there are so many cars in the chart and they are pretty close on the chart.