---
title: "HW2"
author: "Alex Makhratchev, Sharon Zhao, Jiadong Chen"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Q1

```{r}
require(tidyr);
```
Formatting Data
```{r}
library(stringr)
nutrient = read.delim("nutrient.txt", header=FALSE)
df <- data.frame(nutrient)
df <- apply(df, 2, FUN=str_squish)
df <- data.frame(df)
cols = c('id','1', '2','3','4','5');
df <- separate(data=df, V1, cols, sep=' ', convert = TRUE)
df <- subset(df, select = -c(id))
head(df)
```

```{r}
apply(df, 2, mean)
apply(df, 2, sd)
```

## Question #2

Calcium, p is < 0.05, so we reject the hypothesis that the population mean calcium intake is not equal to 1000  
```{r}
t.test(df[1], mu = 1000, alternative = "two.sided")
```

Iron, p is < 0.05, so we reject the hypothesis that the population mean iron intake is not equal to 15  
```{r}
t.test(df[2], mu = 15, alternative = "two.sided")
```
Protein, p is < 0.05, so we reject the hypothesis that the population mean iron intake is not equal to 15 
```{r}
t.test(df[3], mu = 60, alternative = "two.sided")
```

Vitamin A, p is > 0.05, so we accept the hypothesis that the population mean vitamin a intake not equal
```{r}
t.test(df[4], mu = 800, alternative = "two.sided")
```

Vitamin C, p is > 0.05, so we accept the hypothesis that the population mean vitamin c intake not equal
```{r}
t.test(df[5], mu = 75, alternative = "two.sided")
```

## Question 3
US women do not meet the recommended daily nutrient intake amount for Calcium, Iron, Protein, but they do meet it for Vitamin A and C. US women should eat more calcium and iron, but less protein.