---
title: "HW 3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1.1

```{r}
data = read.delim("multiple.txt", sep = " ",header=FALSE)
```

```{r cars}
sample_mean = colMeans(data)
sample_sd = sapply(data, sd)
hnull = hnull = integer(50)

n = nrow(data)
t_statistic = (sample_mean - hnull)/(sample_sd/sqrt(n))

pval = 2*apply(rbind(pt(t_statistic, df = n-1, lower.tail = F),
                     pt(t_statistic, df = n-1, lower.tail = T)), 2, min)
rejection_p <- pval < 0.1
print(pval)
print(rejection_p)

```

## Q1.2

```{r}
alpha = 0.1
FWER = 1 - (1 - alpha)^50
R = sum(rejection_p)
V = sum(rejection_p[11:50])
print(FWER)
print(V/R)
```
FWER: 0.9948462
FDP: 0.2857143

## Q1.3

```{r}
pval.bon = p.adjust(pval, method = "bonferroni")
rejection_bon = pval.bon < 0.1
print(rejection_bon)
FWER.bon = 1 - (1 - alpha/50)^50
print(FWER.bon)
```

FWER: 0.09525318

## Q1.4

```{r}
pval.bh = p.adjust(pval, method = "BH")
rejection_bh = pval.bh < 0.1
alphas = 0.1 * seq(1/50, 1, by = 1/50)
FWER.bh = 1 - prod(1 - alphas)
FDP_bh = sum(rejection_bh[11:50])/sum(rejection_bh)
print(FWER.bh)
print(FDP_bh)
```

BH's FWER is slightly lower than step1 and way higher than step2 but BH's FDP is 0, which is way lower than step1 and 3.


## Q2

The null hypothesis is that the population means of all six variables are 
the same for the genuine and counterfeit bank notes. The alternative
hypothesis is that they are different. We can assume that they have the same population variance-covariance matrices. 

```{r}
library(glue)
banknotes <- read.delim("SwissBankNotes.txt", sep = "")
df <- banknotes
genuine <- df[0:100,]
counterfeit <- df[101:200,]
n <- 100
delta <- colMeans(genuine) - colMeans(counterfeit)
p <- 6
Sg <- cov(genuine)
Sc <- cov(counterfeit)
S_pooled <- ((n-1)*Sg + (n-1)*Sc) / (n+n-2)
t_squared <- (n*n)/(n+n) * t(delta) %*% solve(S_pooled) %*% (delta)
f_statistic <- t_squared * (n+n-p-1)/(p*(n+n-2))
cv <- qf(0.05, p, n+n-p-1, lower.tail = FALSE)
print(glue("The F statistic is {f_statistic} and the critical value is {cv}"))
```

Since the F statistic is larger than the critical value, we are able to 
reject the null hypothesis. We have evidence that the counterfeits are 
distinguishable from the genuine bank notes on at least one of the variables.


