---
title: "finalalex"
output: pdf_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

Loading data
```{r}
train = read.table("spam-train.txt",header=FALSE, sep=",")
head(train)
```

```{r}
test = read.table("spam-test.txt",header=FALSE, sep=",")
head(test)
```
# Standardizing

Standardizing Train Data
```{r}
train_Standardized = data.frame(scale(train))
train_Standardized$V58 = train$V58
train_Standardized
```

Standardizing Test Data
```{r}
test_Standardized = data.frame(scale(test))
test_Standardized$V58 = test$V58
head(test_Standardized)
```

# A) Visualizing Standardized columns

Training Standardized Spam Data V$58 == 1
```{r}
spamStandTrain = train_Standardized[train_Standardized$V58 == 1,]
hist(spamStandTrain$V53,main="Number of times the Charater $ Appears", xlab="$ Character  Appearance")
```
Training Standardized Not Spam Data V$58 == 0
```{r}
NotspamStandTrain = train_Standardized[train_Standardized$V58 == 0,]
hist(NotspamStandTrain$V53,main="Number of times the Charater $ Appears", xlab="$ Character  Appearance")
```
# Log Transformation

Log Transformation on Train Data

```{r}
train_Log = data.frame(log(train+1))
train_Log$V58 = train$V58
head(train_Log)
```

Log Transformation on Test Data

```{r}
test_Log = data.frame(log(test+1))
test_Log$V58 = test$V58
head(test_Log)
```
# Visualizing Log Transformation
0 = Not Spam, 1 = Spam
```{r}
plot(train_Log$V56, train_Log$V57, col=factor(train_Log$V58),xlab="Log of length of the longest uninterrupted
sequence of capital letters", ylab="Log of sum of the lengths of uninterrupted
sequences of capital letters",main="Log of Longest Capital Letters vs. Sum of number of capital letters")
legend("bottomright",
       legend = levels(factor(train_Log$V58)),
       pch = 19,
       col = factor(levels(factor(train_Log$V58))))
```



# Discretize Transformation

Discretize Transformation on Train Data

```{r cars}
train_Discretize = data.frame(train>0)
train_Discretize$V58 = train$V58
train_Discretize = train_Discretize*1
head(train_Discretize)
```

Discretize Transformation on Test Data

```{r cars}
test_Discretize = data.frame(test>0)
test_Discretize$V58 = test$V58
test_Discretize = test_Discretize*1
head(test_Discretize)
```

# Visualization of Discretized Transformed Data
First five columns are if the words "make", "address", "all", "3d", "our" are present in the email.
```{r cars}
discLabels = c("make", "address", "all", "3d", "our")
means = c(mean(train_Discretize$V1),mean(train_Discretize$V2),mean(train_Discretize$V3),mean(train_Discretize$V4),mean(train_Discretize$V5))

barplot(means, main="Ratio of a word being present in all of the training emails",names.arg = discLabels,
   xlab="Word")
```
# B) Logistic Regression Model





