---
title: "finalalex"
output: pdf_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
library(MASS)
```

## Question 1

Loading data
```{r}
train = read.table("spam-train.txt",header=FALSE, sep=",")
head(train)
```

```{r}
test = read.table("spam-test.txt",header=FALSE, sep=",")
head(test)
```
# Standardizing

Standardizing Train Data
```{r}
train_Standardized = data.frame(scale(train))
train_Standardized$V58 = train$V58
train_Standardized
```

Standardizing Test Data
```{r}
test_Standardized = data.frame(scale(test))
test_Standardized$V58 = test$V58
head(test_Standardized)
```

# A) Visualizing Standardized columns

Training Standardized Spam Data V$58 == 1
```{r}
spamStandTrain = train_Standardized[train_Standardized$V58 == 1,]
hist(spamStandTrain$V53,main="Number of times the Charater $ Appears", xlab="$ Character  Appearance")
```
Training Standardized Not Spam Data V$58 == 0
```{r}
NotspamStandTrain = train_Standardized[train_Standardized$V58 == 0,]
hist(NotspamStandTrain$V53,main="Number of times the Charater $ Appears", xlab="$ Character  Appearance")
```
# Log Transformation

Log Transformation on Train Data

```{r}
train_Log = data.frame(log(train+1))
train_Log$V58 = train$V58
head(train_Log)
```

Log Transformation on Test Data

```{r}
test_Log = data.frame(log(test+1))
test_Log$V58 = test$V58
head(test_Log)
```
# Visualizing Log Transformation
0 = Not Spam, 1 = Spam
```{r}
plot(train_Log$V56, train_Log$V57, col=factor(train_Log$V58),xlab="Log of length of the longest uninterrupted
sequence of capital letters", ylab="Log of sum of the lengths of uninterrupted
sequences of capital letters",main="Log of Longest Capital Letters vs. Sum of number of capital letters")
legend("bottomright",
       legend = levels(factor(train_Log$V58)),
       pch = 19,
       col = factor(levels(factor(train_Log$V58))))
```



# Discretize Transformation

Discretize Transformation on Train Data

```{r}
train_Discretize = data.frame(train>0)
train_Discretize$V58 = train$V58
train_Discretize = train_Discretize*1
head(train_Discretize)
```

Discretize Transformation on Test Data

```{r}
test_Discretize = data.frame(test>0)
test_Discretize$V58 = test$V58
test_Discretize = test_Discretize*1
head(test_Discretize)
```

# Visualization of Discretized Transformed Data
First five columns are if the words "make", "address", "all", "3d", "our" are present in the email.
```{r}
discLabels = c("make", "address", "all", "3d", "our")
means = c(mean(train_Discretize$V1),mean(train_Discretize$V2),mean(train_Discretize$V3),mean(train_Discretize$V4),mean(train_Discretize$V5))

barplot(means, main="Ratio of a word being present in all of the training emails",names.arg = discLabels,
   xlab="Word")
```

# C) LDA and QDA 

LDA on the standardized data 
```{r}
stan_model <- lda(V58~., data=train_Standardized)
stan_predictions <- predict(stan_model, test_Standardized)
stan_class = stan_predictions$class
stan_true_val = test_Standardized$V58
stan_test_error = mean(stan_class!=stan_true_val)
stan_test_error
```

LDA on the log transformed data 
```{r}
log_model <- lda(V58~., data=train_Log)
log_predictions <- predict(log_model, test_Log)
log_class = log_predictions$class
log_true_val = test_Log$V58
log_test_error = mean(log_class!=log_true_val)
log_test_error
```

QDA on the standardized data 
```{r}
stan_qda <- qda(V58~., data=train_Standardized)
stan_qdaPred <- predict(stan_qda, test_Standardized)
stan_qdaClass = stan_qdaPred$class
stan_qdaTrue = test_Standardized$V58
stan_qdaTest = mean(stan_qdaClass != stan_qdaTrue)
stan_qdaTest
```

QDA on the transformed data 
```{r}
log_qda = qda(V58~., data=train_Log)
log_qdaPred = predict(log_qda, test_Log)
log_qdaTest = mean(log_qdaPred$class != test_Log$V58)
log_qdaTest
```

Test error rates in a table 
```{r}
tab <- matrix(c(stan_test_error, stan_qdaTest, 
                log_test_error, log_qdaTest), nrow=4, ncol=1)
colnames(tab) <- c('Test Error Rate')
rownames(tab) <- c('LDA on Standardized Data', 
                   'QDA on Standardized Data', 
                   'LDA on Log Transformed Data',
                   'QDA on Log Transformed Data')
tab <- as.table(tab)
tab
```
Comment: LDA performed on the log transformed data has the lowest test error rate, while LDA performed on the standardized data has the highest test error rate. Both LDA and QDA are performed considering all the features. This result indicates that whether or not the email is a spam has a better linear relationship with the 57 features after the log transformation. 


