---
title: "HW5"
date: "2/10/2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Q1

\(a\)

```{r standardized}
data <- read.delim("Places_Rated.txt", header =FALSE, sep = '')
df <- data.frame(data)
names(df) <- c("Climate and Terrain", "Housing", 
               "Health Care & the Environment", "Crime", 
               "Transportation", "Education", "The Arts", 
               "Recreation", "Economics", "index")
standard_df <- scale(df)
standard_cov <- cov(standard_df)
standard_ev <- eigen(standard_cov)
standard_prop <- c()
for ( i in 1:10) {
  prop <- (standard_ev$values[i]) / (sum(standard_ev$values))
  standard_prop <- append(standard_prop, prop)
}
standard_cprop <- c()
cprop <- 0
for ( i in 1:9) {
  cprop <- cprop + standard_prop[i] 
  standard_cprop <- append(standard_cprop, cprop)
}

plot(standard_prop, xlab="Principal Component", 
     ylab="Proportion of Variance Explained", 
     ylim=c(0,1), xaxt="n", type='b', cex=2, pch=20, cex.lab=1.5)
plot(standard_cprop, xlab="Principal Component", 
     ylab="Cumulative Proportion of Variance Explained", 
     ylim=c(0,1), xaxt="n", type="b", col="blue", cex=2, 
     pch=20, cex.lab=1.5)
```

```{r raw}
raw_cov <- cov(df)
raw_ev <- eigen(raw_cov)
raw_prop <- c()
for ( i in 1:10) {
  prop <- (raw_ev$values[i]) / (sum(raw_ev$values))
  raw_prop <- append(raw_prop, prop)
}
raw_cprop <- cumsum(raw_prop[1:9])

plot(raw_prop, xlab="Principal Component", 
     ylab="Proportion of Variance Explained", ylim=c(0,1), 
     xaxt="n", type='b', cex=2, pch=20, cex.lab=1.5)
plot(raw_cprop, xlab="Principal Component", 
     ylab="Cumulative Proportion of Variance Explained", 
     ylim=c(0,1), xaxt="n", type="b", col="blue", cex=2, 
     pch=20, cex.lab=1.5)
```



\(b\)
```{r principal component analysis}
library("ggplot2")
library("ggfortify")
pca_result <- prcomp(df[,1:5], scale=TRUE)
pca_result$rotation
autoplot(pca_result, data=df, color='black')
biplot(pca_result, scale=0)
```

## Question #2
```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
```

```{r}
summary(Weekly)
```

From the numerical summary, we can see that all of the legs have a positive median and mean, signifying on average the stock market grows in a positive direction. This is also evident from the direction variable, with there being significantly more weeks where there was a net positive change.

```{r}
plot(Weekly$Today, Weekly$Volume)
```

From the plot we can see that that if there is a significant change in the price during the week, it would most likely be neagtive. Also, weeks with larger volumes have larger changes in price.

```{r}
plot(Weekly$Lag5, Weekly$Today)
```
From the graph there is minimal correlation between the past 5 weeks of the market and how the market will do this week.

## Question 2b)

```{r}
glm.fit <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data = Weekly, family = binomial)
summary(glm.fit)
```
None of the variables seem statistically significant, but Lag2 seems to be the most useful out of all of them.

## Question 2c
```{r}
Probs = predict(glm.fit, type='response')
contrasts(Weekly$Direction)
Pred_trend = ifelse(Probs>0.5, "Up", "Down")
table(Pred_trend, Weekly$Direction)
mean(Pred_trend == Weekly$Direction)
```
Fraction of correct predict is 0.561. This model is predicting to much "up" since the dataset is unbalanced.

## Question 2d
```{r}
Data_train = Weekly[Weekly$Year <= 2008,]
Data_test = Weekly[Weekly$Year > 2008,]
glm_fits2 = glm(Direction ~ Lag2, data = Data_train, family = binomial)
Probs_2 = predict(glm_fits2, Data_test, type = "response")
Pred_trend2 = ifelse(Probs_2>0.5, "Up", "Down")
table(Pred_trend2, Data_test$Direction)
```
```{r}
mean(Pred_trend2 == Data_test$Direction)
```