---
title: "hw5alex"
author: "alex"
date: "2/11/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ISLR)
```

## Question #2

```{r cars}
summary(Weekly)
```

From the numerical summary, we can see that all of the legs have a positive median and mean, signifying on average the stock market grows in a positive direction. This is also evident from the direction variable, with there being significantly more weeks where there was a net positive change.

```{r cars}
plot(Weekly$Today, Weekly$Volume)
```

From the plot we can see that that if there is a significant change in the price during the week, it would most likely be neagtive. Also, weeks with larger volumes have larger changes in price.

```{r cars}
plot(Weekly$Lag5, Weekly$Today)
```
From the graph there is minimal correlation between the past 5 weeks of the market and how the market will do this week.

## Question 2b)

```{r cars}
glm.fit <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data = Weekly, family = binomial)
summary(glm.fit)
```
None of the variables seem statistically significant, but Lag2 seems to be the most useful out of all of them.

## Question 2c
```{r}
Probs = predict(glm.fit, type='response')
contrasts(Weekly$Direction)
Pred_trend = ifelse(Probs>0.5, "Up", "Down")
table(Pred_trend, Weekly$Direction)
mean(Pred_trend == Weekly$Direction)
```
Fraction of correct predict is 0.561. This model is predicting to much "up" since the dataset is unbalanced.

## Question 2d
```{r}
Data_train = Weekly[Weekly$Year <= 2008,]
Data_test = Weekly[Weekly$Year > 2008,]
glm_fits2 = glm(Direction ~ Lag2, data = Data_train, family = binomial)
Probs_2 = predict(glm_fits2, Data_test, type = "response")
Pred_trend2 = ifelse(Probs_2>0.5, "Up", "Down")
table(Pred_trend2, Data_test$Direction)
```
```{r}
mean(Pred_trend2 == Data_test$Direction)
```